Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-10-13 parts/massmodel.tex
working on letter2
small edits

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the image locations, parities and time
ordering, given by the modeller.  The mass maps are made up of mass
tiles and are free-form, but are required to be concentrated around
the identified lens centre \citep[see][for the precise formulation of
the search problem]{2014MNRAS.445.2181C}.  The modeller can also set
various options for the search, such as the number of mass tiles and
the extent of the mass map; all options have defaults.  Typically,
there are $\sim$ 500 mass tiles arranged in a disc, centred on the
lensing galaxy and extending to twice the radius of the outermost
image.  By default, the mass distributed is required to have
$180^\circ$ rotation symmetry, but this option can be unset.  Assuming
mass distributions can be found -- which in practice is usually the
case -- a statistical ensemble of two-dimensional mass maps is
returned.  
This ensemble of typically 200 models, along with derived quantities and uncertainties, makes up one SpaghettiLens model.
Each of these ensemble of models is usually represented using tile-by-tile mean values and uncertainties derived from tile-by-tile minima and maxima.

>>>>

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the image locations, parities and time
ordering, given by the modeller.  The mass maps are made up of mass
tiles and are free-form, but are required to be concentrated around
the identified lens centre \citep[see][for the precise formulation of
  the search problem]{2014MNRAS.445.2181C}.  The modeller can also set
various options for the search, such as the number of mass tiles and
the extent of the mass map; all options have defaults.  Typically,
there are $\sim500$ mass tiles arranged in a disc, centred on the
lensing galaxy and extending to twice the radius of the outermost
image.  By default, the mass distributed is required to have
$180^\circ$ rotation symmetry, but this option can be unset.  Assuming
mass distributions can be found -- which in practice is usually the
case -- a statistical ensemble of 200 two-dimensional mass maps is
returned.  From each mass map, further quantities such as lens
potentials or enclosed masses can be derived.  Thus, there are
ensembles of 200 values for the surface density at any point, for the
enclosed mass within a given radius and so on.  In this paper we
present the averages and ranges of different quantities, but other
quantities such as 90\% confidence ranges could also be computed.  The
whole ensemble of mass maps, along with derived quantities and
uncertainties, makes up one SpaghettiLens model.
